BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-12-26 Paper/BOAST.tex
abstract

\address[lig]{Laboratoire d'Informatique de Grenoble}
\address[cnrs]{Centre National de la Recherche Scientifique}
\address[cea]{CEA/INAC/SP2M/L\_Sim}
\address[ujf]{Université Joseph Fourier}
\address[inria]{Inria}
\begin{abstract}
The portability of real HPC applications on new platforms is an open and very
delicate problem.  Especially the performance portability of the underlying
computing kernels, is problematic as they need to be tuned for each and every
platform the application encounters.  This paper presents BOAST, a
metaprogramming framework dedicated computing kernels.  BOAST allows the
description of a kernel and its possible optimizations using a DSL.  BOAST
runtime will then compare the different version's performance as well as verify
their exactness. BOAST is applied to three use cases: a Laplace kernel in
OpenCL, and two HPC applications BigDFT (electronic density computation) and
SPECFEM3D (seismic and wave propagation).
\end{abstract}

>>>>

\address[lig]{Laboratoire d'Informatique de Grenoble}
\address[cnrs]{Centre National de la Recherche Scientifique}
\address[cea]{CEA/INAC/SP2M/L\_Sim}
\address[ujf]{Université Joseph Fourier}
\address[inria]{Inria}
\begin{abstract}
The portability of real HPC applications on new platforms is an open and very
delicate problem.  Especially the performance portability of the underlying
computing kernels is problematic as they need to be tuned for each and every
platform the application encounters. This paper presents BOAST, a
metaprogramming framework dedicated to computing kernels.  BOAST allows the
description of a kernel and its possible optimizations using a DSL. BOAST
runtime will then compare the different versions' performance as well as verify
their exactness. BOAST is applied to three use cases: a Laplace kernel in
OpenCL and two HPC applications BigDFT (electronic density computation) and
SPECFEM3D (seismic and wave propagation).
\end{abstract}
